---
title: "Knitting hats, scarves, and mittens"
author: "Alison Hill"
output:
  distill::distill_article:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, fig.path="figs/")
```

## Data

http://langcog.github.io/wordbankr/

## Packages

```{r}
library(tidyverse)
library(wordbankr)
library(here)
library(paletteer)
library(prismatic)
ggplot2::theme_set(theme_minimal())
```

## Getting knitted things

```{r}
clothing <- get_item_data(
  language = "English (American)", 
  form = "WS"
  ) %>%
  filter(category == "clothing")

# selecting hat / scarf / mittens
knitted_things <- c("hat", "scarf", "mittens")

# get the items for my selected knitted things
my_knits <- get_item_data(
  language = "English (American)", 
  form = "WS"
  ) %>%
  filter(definition %in% knitted_things) 
```

```{r}
my_knits
```


## Get word production data

Can I get median total vocab size? 

```{r}
# then get instrument data for those items
words <- get_instrument_data(
  language = "English (American)",
  form = "WS",
  items = my_knits$item_id,
  administrations = TRUE,
  iteminfo = TRUE
  ) %>% 
  mutate(produces = value == "produces") %>% 
  select(-value) %>% 
  drop_na(produces) %>%
  filter(type == "word", !is.na(uni_lemma))
```

```{r}
words
```



## Check licenses

```{r}
words %>% 
  distinct(license)
```


## Summarize

What proportion of kids at each age produce each word?

```{r}
word_summary <- words %>% 
  group_by(age, uni_lemma) %>%
  summarise(kids_produce = sum(produces, na.rm = TRUE),
            kids_n = n_distinct(data_id),
            prop_produce = kids_produce / kids_n) %>% 
  ungroup() %>% 
  # grab even ages only
  filter(age %% 2 == 0) %>% 
  select(age, lemma = uni_lemma, prop_produce, kids_n)
```

```{r}
word_summary
```


## Age distribution

```{r ages}
ggplot(filter(word_summary, lemma == "scarf"), 
       aes(x = age, y = kids_n)) +
  geom_col(fill = "darkcyan", alpha = .5, width = 2)
```



## Line plot

```{r lineplot}
words_line <-
  ggplot(word_summary, aes(x = age, y = prop_produce, color = lemma)) + 
  geom_smooth(se = FALSE, lwd = .5) +
  geom_point(size = 2)  +
  labs(x = "Age (months)", y = "Proportion of Children Producing") 
words_line
```

## Play with color on line plots

```{r saguaro}
words_line + scale_color_paletteer_d("nationalparkcolors::Saguaro")
```

```{r badlands}
words_line + scale_color_paletteer_d("nationalparkcolors::Badlands")
```

```{r picasso}
words_line + scale_color_paletteer_d("lisa::PabloPicasso")
```

```{r chagall}
words_line + scale_color_paletteer_d("lisa::MarcChagall")
```

## Check colorblindness

```{r}
paletteer_d("nationalparkcolors::Badlands", n = 3) %>%
  prismatic::check_color_blindness()
```

```{r}
paletteer_d("nationalparkcolors::Saguaro", n = 3) %>%
  prismatic::check_color_blindness()
```

```{r}
paletteer_d("colorblindr::OkabeIto", n = 3) %>%
  prismatic::check_color_blindness()
```

## Better for colorblind

```{r colorblind}
words_line + scale_color_paletteer_d("colorblindr::OkabeIto")
```

## Play with more plots

### Bar plot

```{r barplot}
ggplot(word_summary, aes(x = age, y = prop_produce)) +
  geom_col(aes(fill = lemma), alpha = .8, 
           position = "identity") +
  scale_fill_paletteer_d("colorblindr::OkabeIto") 
```

### Facetted bar plot

```{r facet}
ggplot(word_summary, aes(x = age, y = prop_produce)) +
  geom_col(aes(fill = lemma), alpha = .8) +
  scale_fill_paletteer_d("colorblindr::OkabeIto", guide = FALSE) + 
  facet_wrap(~lemma)
```

### Dodged bar plot

```{r dodgeplot}
ggplot(word_summary, aes(x = age, y = prop_produce)) +
  geom_col(aes(fill = lemma), alpha = .8, position="dodge") +
  scale_fill_paletteer_d("colorblindr::OkabeIto") 
```

### Rose chart

```{r}
words_rose <-
  ggplot(word_summary, 
         aes(x = age, y = prop_produce, fill = lemma)) +
  geom_col(width = 2) +
  coord_polar() 
```

```{r rosesaguaro}
words_rose + 
  scale_fill_paletteer_d("nationalparkcolors::Saguaro") + 
  theme(axis.text.y = element_blank())
```

```{r roseeverglades}
words_rose + 
  scale_fill_paletteer_d("nationalparkcolors::Everglades") + 
  theme(axis.text.y = element_blank())
```


## Crosslinguistic data

Could be great for parameters, or facetting?

```{r cache=TRUE}
knitted_langs <- get_crossling_data(uni_lemmas = knitted_things)
```

```{r cache=TRUE}
knitted_langs %>% 
  # grouped already? that is tricky
  ungroup() %>% 
  filter(n_children > 100) %>% 
  distinct(language)

# oof item ids are different
knitted_langs %>% 
  # grouped already? that is tricky
  ungroup() %>% 
  filter(n_children > 100) %>% 
  distinct(item_id, language, uni_lemma, definition)
```

## Exporting

Now let's export both data frames.

```{r}
write_csv(words, 
          here::here("data","words.csv"))
write_csv(word_summary, 
          here::here("data","word_summary.csv"))
```

